### 2017-10-09 Gruba/03-fe.tex

\section{Feature Extractor}
\label{sec:fe}

@@

\begin{table}[!htb]
\centering
\caption{Illustration of Variables in Info Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_s$				& number of followers				\\	\midrule
\#$E_s$				& number of followees				\\	\midrule
\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
 						&                       									\\	\midrule
\#$B_s$				& number of blogs owned by the user				\\	\midrule
\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
 						&                       									\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule              
\end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{Category of Info}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
0                       & $\#E_s \le 50 \ \& \ \#R_s \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_s}{\#R_s} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_s}{\#E_s} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule              
\end{tabular}
\end{table}

@@

\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF \refe{} to calculate the weight distribution of words in blog $b$: 
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.

>>>>

\section{Feature Extraction}
\label{sec:fe}

@@

\begin{table}[!htb]
\centering
\begin{small}
\caption{Illustration of Variables in Info Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_s$				& number of followers				\\	\midrule
\#$E_s$				& number of followees				\\	\midrule
\multirow{2}{*}{$R_{ee}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#R_s}{\#E_s}$}	\\
 						&                       									\\	\midrule
\#$B_s$				& number of blogs owned by the user				\\	\midrule
\multirow{2}{*}{$R_{oc}$}      & \multirow{2}{*}{a ratio defined as $\frac{\#(B_s | R(B)==1)}{\#(B_s | R(B)==0)}$}	\\
 						&                       									\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

\begin{table}[!htb]
\centering
\begin{small}
\caption{Category of Info}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
0                       & $\#E_s \le 50 \ \& \ \#R_s \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_s}{\#R_s} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_s}{\#E_s} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.
